Inter-task effects induce bias in crowdsourcing

### 2014-08-03 docs/publications/2014.05_PNAS/manuscript.tex
add abstract

\title{Inter-task effects introduce bias in crowdsourcing}
\author{Edward Newell, Derek Ruths}

@@

\begin{document}
\maketitle
\section*{Abstract}
\section*{Significance Statement}
\section*{Introduction}

>>>>

\title{Inter-task effects induce bias in crowdsourcing}
\author{Edward Newell, Derek Ruths}

@@

\begin{document}
\maketitle
\section*{Abstract}
Microtask platforms like Amazon Mechanical Turk provide a cheap and fast means
to engage participants for scientific reasearch.  
Workers on such platforms prefer to work on batches of tasks of the same 
type[***], so we investigate the potential for the content of earlier tasks 
to influence worker performance in later tasks, which we call ``inter-task'' 
effects.  
Existing research investigates the impact of various design factors, such as 
``framing'', on the quality of crowdsourced content, but does not, to 
our knowledge, address inter-task effects.  
We employ a canonical image-labeling task on the Amazon Mechanical Turk 
platform, to measure both inter-task and framing effects, in terms of their 
impact to the content and specificity of the labels workers provide.
We also introduce an algorithmic definition of priming, which measures the 
worst-case bias that priming effects introduce into crowdsourced content.
We find that inter-task effects produce a much stronger impact than framing, 
and find that our algorithmic definition yields a powerful, generalized measure
for priming effects when combined with machine learning algorithms.

\section*{Significance Statement}
\section*{Introduction}
